The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-19 paper.tex
minor changes

In this section we will try to create a common ground in the understanding of anthropomorphism since we have found conflicting definitions of the term. We first present anthropomorphism as a social phenomenon. Then we propose to use another term, namely ``anthropomorphic form'', to refer to the human-inspired design of artifacts. Finally, we focus on both anthropomorphism and anthropomorphic design in human-robot interaction / robotics, as here both topics are brought together naturally.

@@

Anthropomorphism is an interesting phenomenon because it tells us something about the relationship between the human who anthropomorphizes, and the non-human agent which is anthropomorphized. Though commonly observed, it appears controversial, at the same time, that humans tend to perceive human-like physical appearance (\eg faces), emotional states, or inner mental states and motivations in non-human agents such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).

Originally, the term \textbf{anthropomorphism} comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form / structure' (or `shape'). Anthropomorphism is generally understood as people's tendency to perceive a non-human agent as if it had some human characteristics or traits. In turn, how a person perceives an agent further determines how she relates to and behaves towards the agent, or how she may behave in light of this agent \citep{epley_when_2008}.
As such, anthropomorphism can be seen as a special kind of relationship between a human interacting with a non-human agent. This anthropomorphic relationship is often characterized by the fact that the human attributes or ascribes human-unique characteristics to the non-human agent. Since anthropomorphism becomes observable through these attributions, some definitions claim that anthropomorphism is not the perception but rather the attribution of human attributes to non-human agents, and name thoughts, emotions, and intentions as examples. The most prominently anthropomorphized non-human agents are probably animals and robots \citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.

@@

Not only \cite{epley_when_2008} and \cite{duffy_anthropomorphism_2002} but also others have noticed that anthropomorphism is a very complex phenomenon - in itself, in how it can be understood, and when studying it.
A common formal ground is missing so far; however, it is important to be clear about what exactly we mean when using the term anthropomorphism.

>>>>

In this section we will try to create a common ground in the understanding of anthropomorphism since we have found conflicting definitions of the term. We first present anthropomorphism as a social phenomenon. Then we propose to use another term, namely ``anthropomorphic form'', to refer to the human-inspired design of artifacts. Finally, we focus on both anthropomorphism and anthropomorphic design in human-robot interaction / robotics, as in these domains both topics are brought together naturally. \hl{(adjust according to the section)}

@@

Anthropomorphism is an interesting phenomenon because it tells us something about the relationship between the human who anthropomorphizes, and the non-human agent which is anthropomorphized. Though commonly observed, it appears controversial, at the same time, that humans tend to \hl{\textit{``see something human in the non-human''}}.

Humans tend to perceive human-like characteristics such as physical appearance, emotional states, or inner mental states and motivations in non-human agents that do not have these characteristics themselves, such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).

Originally, the term \textbf{anthropomorphism} comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form / structure' (or `shape'). Anthropomorphism is generally understood as people's tendency to perceive a non-human agent as if it had some human characteristics or traits. In turn, how a person perceives an agent further determines how she relates to and behaves towards the agent, or how she may behave in light of this agent \citep{epley_when_2008}.
As such, anthropomorphism can be seen as a special kind of relationship between a human interacting with a non-human agent. This anthropomorphic relationship is often characterized by the fact that the human attributes human-unique characteristics to the non-human agent. Since anthropomorphism becomes observable through these attributions, some definitions claim that anthropomorphism is not the perception but rather the attribution of human attributes to non-human agents, and name thoughts, emotions, and intentions as examples. The most prominently anthropomorphized non-human agents are probably animals and robots \citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.

@@

Not only \cite{epley_when_2008} and \cite{duffy_anthropomorphism_2002} but also others have noticed that anthropomorphism is a very complex phenomenon -- itself and in how it can be understood. This holds implications for the study of anthropomorphism (to what we will come back later in this article \hl{(REF to studying / measuring anthropomorphism)}.
A common formal ground is missing so far; however, it is important to be clear about what exactly we mean when using the term anthropomorphism.
